### 2013-12-13 paper_draft.tex
last changes to affiliations & text. with rebuttal

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp E. Bayer$^{2,3}$, 
Helge Rausch$^{4}$,
Julia Reda$^{5}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} School of Land, Crop and Food Sciences and Australian Centre for Plant Functional Genomics, University of Queensland, Brisbane, Australia
\\
\bf{3} Australian Centre for Plant Functional Genomics, School of Agriculture and Food Sciences, University of Queensland, Brisbane, Australia
\\
\bf{4} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{5} Johannes Gutenberg University Mayence, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Ethics Statement}
In line with the German regulations and the ethics approval system for biomedical studies \cite{Pinkerton2002} we contacted the ethics commission of the Goethe University Frankfurt am Main, Germany teaching hospital. The director of it confirmed that this study does not fall within their remit.

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,2,\ast}$, 
Philipp E. Bayer$^{3,4}$, 
Helge Rausch$^{5}$,
Julia Reda$^{6}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} Department for Applied Bioinformatics, Institute for Cell Biology and Neuroscience, Goethe University Frankfurt am Main, Germany 
\\
\bf{3} School of Land, Crop and Food Sciences and Australian Centre for Plant Functional Genomics, University of Queensland, Brisbane, Australia
\\
\bf{4} Australian Centre for Plant Functional Genomics, School of Agriculture and Food Sciences, University of Queensland, Brisbane, Australia
\\
\bf{5} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{6} Johannes Gutenberg University Mainz, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Ethics Statement}
In line with the German regulations and the ethics approval system for biomedical studies \cite{Pinkerton2002} we contacted the ethics commission of the Goethe University Frankfurt am Main, Germany teaching hospital. Its director confirmed that this study does not fall within their remit.
